---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# anMC

`anMC` is a R package to efficiently compute orthant probabilities of high-dimensional Gaussian vectors. The method is applied to compute conservative estimates of excursion sets of functions under Gaussian random field priors. This is an upgrade on the previously existent package [ConservativeEstimates][consEst-reference]. See the paper [Azzimonti, D. and Ginsbourger D. (2018)][article-reference] for more details.

### Features

The package main functions are:

* `ProbaMax`: the main function for high dimensional othant probabilities. Computes _P(max X > t)_, where _X_ is a Gaussian vector and _t_ is the selected threshold. The function computes the probability with the decomposition explained [here][article-reference]. It implements both the `GMC` and `GANMC` algorithms. It allows user-defined functions for the core probability estimate (defaults to `pmvnorm` of the package `mvtnorm`) and the truncated normal sampler (defaults to `trmvrnorm_rej_cpp`) required in the method.

* `ProbaMin`: analogous of `ProbaMax` but used to compute _P(min X < t)_, where _X_ is a Gaussian vector and _t_ is the selected threshold. This function computes the probability with the decomposition explained [here][article-reference]. It implements both the `GMC` and `GANMC` algorithms.

* `conservativeEstimate` : the main function for conservative estimates computation. Requires the mean and covariance of the posterior field at a discretization design.



### Installation

To install the latest version of the package run the following code from a R console:

```{r,echo=TRUE,eval=FALSE}
if (!require("devtools"))
  install.packages("devtools")
devtools::install_github("dazzimonti/anMC")
```


### References

Azzimonti, D. and Ginsbourger, D. (2018). Estimating orthant probabilities of high dimensional Gaussian vectors with an application to set estimation. Journal of Computational and Graphical Statistics, 27(2), 255-267. [DOI: 10.1080/10618600.2017.1360781][doi-article]. Preprint at [hal-01289126][article-reference]

Azzimonti, D. (2016). Contributions to Bayesian set estimation relying on random field priors. PhD thesis, University of Bern. Available at [link][thesis-reference]

[doi-article]: https://doi.org/10.1080/10618600.2017.1360781
[article-reference]: https://hal.archives-ouvertes.fr/hal-01289126
[consEst-reference]: https://github.com/dazzimonti/ConservativeEstimates
[thesis-reference]: http://biblio.unibe.ch/download/eldiss/16azzimonti_d.pdf
